15th International Satisfiability Modulo Theories Competition (SMT-COMP 2021): Rules and Procedures

### 2021-05-07 rules/rules21.tex
Cloud track explicitly marked experimental
Added notes on cloud & parallel tracks in benchmark scoring

\header{Benchmark Selection.}
We will select non-incremental benchmarks from the smt-lib divisions
based on the participating solvers.  In total 500 instances will be
chosen such that their run times are sufficiently high based on our
estimation.  The track will be experimental.

@@

\subsection{\cloudtrack{}}
The \cloudtrack{} will evaluate the capability of solvers to determine
the satisfiability of problems in a distributed computing environment.

@@

\header{Divisions.}

Within each track there are multiple divisions, and each division selects
benchmarks from a specific group of SMT-LIB logics in the SMT-LIB benchmark
library.

@@

\header{Benchmark selection.} \label{benchmark-selection}
The competition will use a large subset of SMT-LIB benchmarks, with some
guarantees on including new benchmarks.  In \textbf{all} tracks
% \textbf{except} the \challtrack,
the following selection process will be used.
\begin{enumerate}
\item \emph{Remove inappropriate benchmarks.} The
  organizers may remove benchmarks that are deemed inappropriate or
  uninteresting for competition, or cut the size of certain benchmark
  families to avoid their over-representation.  SMT-COMP attempts to
  give preference to benchmarks that are ``real-world,'' in the sense
  of coming from or having some intended application outside SMT.
\item \emph{Remove easy / uninteresting benchmarks.}
  For the following tracks, all benchmarks that can be
  considered as easy or uninteresting based on the following criteria
  will be removed.
  \begin{itemize}
    \item \emph{\maintrack.} All benchmarks that were solved by all
      solvers (including non-competitive solvers) in less than one second in
          the corresponding track in 2018, 2019, and 2020.
    \item \emph{\ucoretrack.} All benchmarks with only a single assertion.
  \end{itemize}
\item \emph{Cap the number of instances in a division.}
  The number of benchmarks in a division based on the size of the
  corresponding logics in SMT-LIB will be limited as follows.
  Let $n$ be the number of benchmarks in an SMT-LIB logic, then
  \begin{enumerate}
  \vspace{-1ex}
    \item \label{bench-sel-300} if $n \le 300$, all instances will be selected;
  \item \label{bench-sel-600} if $300 < n \leq 750$, a subset of 300 instances
    from the logic will be selected;
  \item \label{bench-sel-more} and if $n > 750$,
      40\% of the benchmarks of the logic will be selected.
  \end{enumerate}
\end{enumerate}
%
The selection process in cases \ref{bench-sel-600} and \ref{bench-sel-more}
above will guarantee the inclusion of new benchmarks by first picking randomly
one benchmark from each new benchmark family.  The rest of the benchmarks will
be chosen randomly from the remaining benchmarks using a uniform distribution.
%
The benchmark selection script will be publicly available at
\url{https://github.com/SMT-COMP/smt-comp/tree/master/tools} and
will use the same random seed as the rest of the competition.  The set of
benchmarks selected for the competition will be published when the competition
begins.

@@

\header{Error Score ($\mathbf{e}$).}
For the \maintrack, and \inctrack,%
% and \challtrack
$e$ is the number of returned
statuses that disagree with the given expected status (as described above,
disagreements on benchmarks with unknown status lead to the benchmark being
disregarded). For the \ucoretrack, $e$ includes, in addition, the number of
returned unsat cores that are not, in fact, unsatisfiable (as
validated by a selection of other solvers selected by organizers).  For the
\mvaltrack, $e$ includes, in addition, the number of returned models that are
not full satisfiable models.

\header{Correctly Solved Score ($\mathbf{n}$).}
For the \maintrack, \inctrack, and \mvaltrack,
$N$ is defined as the number of \akey{check-sat} commands, and
$n$ is defined as the number of correct results.
For the \ucoretrack, $N$ is defined as the number of named top-level assertions,
and $n$ is defined as the \emph{reduction}, i.e., the difference between $N$
and the size of the unsat core.

>>>>

@@

\subsection{\cloudtrack{}}
The \cloudtrack{} will evaluate the capability of solvers to determine
the satisfiability of problems in a distributed computing environment.
The track will be experimental.

@@

\header{Divisions.}
%
Within each track there are multiple divisions, and each division selects
benchmarks from a specific group of SMT-LIB logics in the SMT-LIB benchmark
library.

@@

\header{Benchmark selection.} \label{benchmark-selection}
The competition will use a large subset of SMT-LIB benchmarks, with some
guarantees on including new benchmarks.  In \textbf{all} tracks
\textbf{except} the \paralleltrack and \cloudtrack
the following selection process will be used.
\begin{enumerate}
\item \emph{Remove inappropriate benchmarks.} The
  organizers may remove benchmarks that are deemed inappropriate or
  uninteresting for competition, or cut the size of certain benchmark
  families to avoid their over-representation.  SMT-COMP attempts to
  give preference to benchmarks that are ``real-world,'' in the sense
  of coming from or having some intended application outside SMT.
\item \emph{Remove easy / uninteresting benchmarks.}
  For the following tracks, all benchmarks that can be
  considered as easy or uninteresting based on the following criteria
  will be removed.
  \begin{itemize}
    \item \emph{\maintrack.} All benchmarks that were solved by all
      solvers (including non-competitive solvers) in less than one second in
          the corresponding track in 2018, 2019, and 2020.
    \item \emph{\ucoretrack.} All benchmarks with only a single assertion.
  \end{itemize}
\item \emph{Cap the number of instances in a division.}
  The number of benchmarks in a division based on the size of the
  corresponding logics in SMT-LIB will be limited as follows.
  Let $n$ be the number of benchmarks in an SMT-LIB logic, then
  \begin{enumerate}
  \vspace{-1ex}
    \item \label{bench-sel-300} if $n \le 300$, all instances will be selected;
  \item \label{bench-sel-600} if $300 < n \leq 750$, a subset of 300 instances
    from the logic will be selected;
  \item \label{bench-sel-more} and if $n > 750$,
      40\% of the benchmarks of the logic will be selected.
  \end{enumerate}
\end{enumerate}
%
The selection process in cases \ref{bench-sel-600} and \ref{bench-sel-more}
above will guarantee the inclusion of new benchmarks by first picking randomly
one benchmark from each new benchmark family.  The rest of the benchmarks will
be chosen randomly from the remaining benchmarks using a uniform distribution.
%
The benchmark selection script will be publicly available at
\url{https://github.com/SMT-COMP/smt-comp/tree/master/tools} and
will use the same random seed as the rest of the competition.  The set of
benchmarks selected for the competition will be published when the competition
begins.

@@

\header{Error Score ($\mathbf{e}$).}
For the \maintrack, \inctrack, \paralleltrack, and \cloudtrack
$e$ is the number of returned
statuses that disagree with the given expected status (as described above,
disagreements on benchmarks with unknown status lead to the benchmark being
disregarded). For the \ucoretrack, $e$ includes, in addition, the number of
returned unsat cores that are not, in fact, unsatisfiable (as
validated by a selection of other solvers selected by organizers).  For the
\mvaltrack, $e$ includes, in addition, the number of returned models that are
not full satisfiable models.

\header{Correctly Solved Score ($\mathbf{n}$).}
For the \maintrack, \inctrack, \mvaltrack, \paralleltrack, and
\cloudtrack,
$N$ is defined as the number of \akey{check-sat} commands, and
$n$ is defined as the number of correct results.
For the \ucoretrack, $N$ is defined as the number of named top-level assertions,
and $n$ is defined as the \emph{reduction}, i.e., the difference between $N$
and the size of the unsat core.
